Project Description

### 2019-05-16 index.Rmd

>>>>

## Abstract

Title: Geodesic distance estimation for functional data residing near a nonlinear manifold.

Abstract: Certain functional data of interest reside in non-linear spaces; the class of probability density functions provides one such example. Since these spaces are not vector spaces, basic operations such as addition and subtraction require special consideration and treatment. In this work we set ourselves the task of calculating a geodesic distance between two functions living near a non-linear manifold due to noise. This setting cannot be tackled by classic manifold learning techniques which require data to live exactly on a manifold. Good estimation of the geodesic distance has implications for many downstream tasks such as clustering, classification, and nonparametric functional regression.

*I wrote this for the IMS China 2019 conference.*
